### 2017-12-10 manuscript.rmd
Fig. 1 legend update
text edits

![Photographs of representatives of the major groups of siphonophores. (A) *Rhisophysa eysenhardtii*, scale bar = 1 cm. (B) *Bathyphysa conifera*, scale bar = XXX. (C) *Hippopodius hippopus*, scale bar = 5 mm. (D) *Physophora hydrostatica*, scale bar = 5 mm. (E) *Nanomia bijuga*, scale bar = 1 cm. (F) *Desmophyes haematogaster*, scale bar = 5 mm. (G) *Sphaeronectes christiansonae*, scale bar = 2 mm. (H) *Lychnagalma utricularia*, scale bar = 1 cm. (I) *Kephyes hiulcus*, scale bar = 2 mm. (J) *Praya dubia*, scale bar = 4 cm . (K) *Apolemia* sp., scale bar = 1 cm.](figures/Figure1.jpg)

@@

Major questions remained after this early work, though. There was, in particular, little support for important deep relationships within Codonophora. Resolving deep relationships within Codonophora is key to resolving the evolution of several traits, including sexual systems (monoecy versus dioecy) or the gain and loss of particular zooids, such as palpons (Fig. 2). Here we present a broadly sampled phylogenomic analysis of Siphonophora, assessing transcriptomic data from 33 siphonophore species and 10 outgroup species (2 outgroups were subsequently excluded). Using 1,071 genes shared across species, we find strong support for several relationships within the siphonophore phylogeny. Using this phylogeny, we reconstruct the evolutionary history of characters central to their unique biology, including zooid type, life history traits, and habitat.

@@

```
These findings are largely consistent with a previous analysis based on two genes (16S and 18S ribosomal RNA) (Fig. 3) [@Dunn:2005dy]. There is strong support for the Cystonectae as sister to all other siphonophores, the Codonophora. We also find strong support for Calycophorae nested within the paraphyletic "Physonectae", and for the Apolemidae as sister to all other codonophorans. Multiple nodes that were not resolved in the previous two-gene analysis receive strong support in this 1,071-gene transcriptome analysis. There is strong support for the Pyrostephidae as sister to all other non-Apolemid codonophorans. Within the clade that is sister to the Pyrostephidae, we find two main clades, the Calycophorae and a clade we call the Euphysonectae (Fig. 3), which includes the remaining non-Apolemid, non-Pyrostephid "Physonectae". We define the Euphysonectae as the clade consisting of *Agalma elegans* and all taxa that are more closely related to it than to *Diphyes dispar*. Within Euphysonectae, we identify Clade A and Clade B (Fig. 3). Clade A is a group of siphonophores that all have an involucrum, or fold, that forms around the base of the tentilla [@totton1965synopsis]. This clade also shares the prescence of a descending mantle canal within the nectophores (Fig. S6). Clade B is a group of deep-sea siphonophores found within the bathypelagic. Within Clade B there is low support for the placement of *Erenna richardi*, and more taxon sampling will be required to determine the relationship of species within this clade.

>>>>

![Photographs of representatives of the three major groups of siphonophores. Cystonectae (A-B), Calycophorae (C-F) and Physonectae (G-K). (A) *Rhisophysa eysenhardtii*, scale bar = 1 cm. (B) *Bathyphysa conifera*, scale bar = 2cm. (C) *Hippopodius hippopus*, scale bar = 5 mm. (D) *Kephyes hiulcus*, scale bar = 2 mm. (E) *Desmophyes haematogaster*, scale bar = 5 mm. (F) *Sphaeronectes christiansonae*, scale bar = 2 mm. (G) *Nanomia bijuga*, scale bar = 1 cm. (H) *Lychnagalma utricularia*, scale bar = 1 cm. (I) *Physophora hydrostatica*, scale bar = 5 mm. (J) *Praya dubia*, scale bar = 4 cm . (K) *Apolemia* sp., scale bar = 1 cm.](figures/Figure1.jpg)

@@

Major questions remained after this early work, though. There was, in particular, little support for important deep relationships within Codonophora. Resolving these relationships is key to resolving the evolution of several traits, including sexual systems (monoecy versus dioecy) or the gain and loss of particular zooids, such as palpons (Fig. 2). Here we present a broadly sampled phylogenomic analysis of Siphonophora, assessing transcriptomic data from 33 siphonophore species and 10 outgroup species (2 outgroups were subsequently excluded). Using 1,071 genes shared across species, we find strong support for several relationships within the group. Using this phylogeny, we reconstruct the evolutionary history of characters central to their unique biology, including zooid type, life history traits, and habitat.

@@

```
These findings are largely consistent with a previous analysis based on two genes (16S and 18S ribosomal RNA) (Fig. 3) [@Dunn:2005dy]. There is strong support for Cystonectae as sister to all other siphonophores, the codonophorans. We also find strong support for Calycophorae nested within the paraphyletic "Physonectae", and for Apolemidae as sister to all other codonophorans. Multiple nodes that were not resolved in the previous two-gene analysis receive strong support in this 1,071-gene transcriptome analysis. There is strong support for Pyrostephidae as sister to all other non-Apolemid codonophorans. Within the clade that is sister to Pyrostephidae, we find two main clades, Calycophorae and a clade we call Euphysonectae (Fig. 3), which includes the remaining non-Apolemid, non-Pyrostephid physonects. We define Euphysonectae as the clade consisting of *Agalma elegans* and all taxa that are more closely related to it than to *Diphyes dispar*. Within Euphysonectae, we identify Clade A and Clade B (Fig. 3). Clade A comprises siphonophores that all have an involucrum, or fold, that forms around the base of the tentilla [@totton1965synopsis]. This clade also shares the prescence of a descending mantle canal within the nectophores (Fig. S6). Clade B is a group of deep-sea siphonophores found within the bathypelagic. Within Clade B there is low support for the placement of *Erenna richardi*, and more taxon sampling will be required to determine the relationship of species within this clade.
